---
title: "Untitled"
author: "schoenmaked"
date: "23 juni 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



library(caret)
library(knitr)
library(randomForest)
library(rpart)
library(rpart.plot)
library(rattle)
library(corrplot)
library(e1071)
library(rmarkdown)

# Download the dataset 
trainUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testUrl  <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"


# Load the dataset into memory
trainingData <- read.csv(url(trainUrl), na.strings = c("NA", "#DIV/0!", ""))
testingData <- read.csv(url(testUrl), na.strings = c("NA", "#DIV/0!", ""))

#
trainingData <- trainingData[, colSums(is.na(trainingData)) == 0]
testingData <- testingData[, colSums(is.na(testingData)) == 0]

# Delete variables that are not related 
trainingData <- trainingData[, -c(1:7)]
testingData <- testingData[, -c(1:7)]

# partioning the training set into two different dataset

traningPartitionData <- createDataPartition(trainingData$classe,  p = 0.7, list = F)
trainingDataSet <- trainingData[traningPartitionData, ]
testingDataSet <- trainingData[-traningPartitionData, ]
dim(trainingData); dim(testingDataSet)


# Prediction model 1 - decision tree
decisionTreeModel <- rpart(classe ~ ., data = trainingDataSet, method = "class")
decisionTreePrediction <- predict(decisionTreeModel, testingDataSet, type = "class")

# Plot Decision Tree
rpart.plot(decisionTreeModel, main = "Decision Tree", under = T, faclen = 0)


# Prediction model 2 - random forest
randomForestModel <- randomForest(classe ~. , data = trainingDataSet, method = "class")
randomForestPrediction <- predict(randomForestModel, testingDataSet, type = "class")

confusionMatrix(randomForestPrediction, testingDataSet$classe)




## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
